HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-08-03 scnn.tex
editing the todo list

\section{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.
    \item (TK) update the README for data zip - file from NP
    \item (NP) Finalise readme on Github code
    \item (Waiting for Zenodo) (NP) Finalize the data on zenodo
    \item TK check part sphere notebook and whole sphere
    \item branch with notebooks with plots (results) NP
    \item NP move the repo to HealpixNet
    \item check if papers which appear as arxiv were not published in a conference or journal
    \item (TK) add info on comparison with histograms, so that it's just a demonstration
    \item TK read the result section
    \item TK check the appendix
    \item (almost done) TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item (almost done) TK read everything
    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings.
    \item uniformize text size in figures
    \item (done! first version done) conclusions
    \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
    \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
    \item (done!) TK read the heat section again
    \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
    \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
\end{itemize}

>>>>

\section{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

    \item (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
    \item (NP+MD)  paragraph on our chosen architecture in the Experiments sections
    \item (TK) add reference to figure (pooling) to the area of orders
    \item (NP+MD) move the Related Work section after the Method section

    \item (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.
    \item (TK) update the README for data zip - file from NP
    \item (NP) Finalise readme on Github code
    \item (Waiting for Zenodo) (NP) Finalize the data on zenodo
    \item TK check part sphere notebook and whole sphere
    \item branch with notebooks with plots (results) NP
    \item NP move the repo to HealpixNet
    \item check if papers which appear as arxiv were not published in a conference or journal
    \item (TK) add info on comparison with histograms, so that it's just a demonstration
    \item TK read the result section
    \item TK check the appendix
    \item (almost done) TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item (almost done) TK read everything
    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings.
    \item uniformize text size in figures
    \item (done! first version done) conclusions
    \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
    \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
    \item (done!) TK read the heat section again
    \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
    \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
\end{itemize}
